%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.6in,top=0.5in,right=0.6in,bottom=0.5in]{geometry} % Document margins
\usepackage{ textcomp }
\name{Scott Werwath} % Your name
\address{2400 Durant Ave, Spens Black 405 \\ Berkeley, California 94720} % Your address
\address{(804)~$\cdot$~380~$\cdot$~1188 \\ swerwath@berkeley.edu \\
github.com/swerwath} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Java, C, HTML5, Ruby, Python, MySQL, \LaTeX \\
Frameworks & Rails, MPI \\
Tools & Emacs, NumPy, Git, Microsoft Excel
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of California, Berkeley} \hfill {\em Expected Graduation: December 2018} \\ 
Bachelor of Science: Electrical Engineering \& Computer Science, Nuclear Engineering\\
GPA: 3.90 (Dean's Honors)\\
Member of American Nuclear Society, member of Engineers Without Borders

{\bf Carnegie Mellon University} \hfill {\em Summer 2014} \\ 
Summer Courses \\
GPA: 4.00
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
\begin{rSubsection}{UC Berkeley Department of Electrical Engineering}{January 2016\textminus Present}{Academic Intern (Lab Assistant)}{Berkeley, CA}
\item Trained students in use of laboratory equipment and NumPy for signal processing
\item Coached students in developing core engineering skills, such as circuit design and soldering.
\item Tested and proofread lab documentation
\end{rSubsection}
\begin{rSubsection}{The Collegiate School}{Summer 2013}{IT Assistant}{Richmond, VA}
\item Imaged and packaged leased iMacs and Chromebooks for return according to leaser's specifications.
\item Deployed new Macbooks for use by students on school network.
\item Oversaw migration and set up of wireless network routers and modems to new building.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Volunteering}

\begin{rSubsection}{Powell Economic Education Foundation}{Fall 2012\textminus Fall 2015}{Website Developer and Database Administrator}{Richmond, VA}
\item Designed, built, and launched a new website for the Foundation using Bootstrap framework for HTML5.
\item Created and managed database for applicants to apply to PEEF's summer internship program using PHP and MySQL.
\item Instructed Foundation faculty in the use of new database system.
\end{rSubsection}
\begin{rSubsection}{The Elk Hill School}{Summer 2012}{Eagle Scout Project}{Charlottesville, VA}
\item Sourced refurbished laptops from a local business.
\item Managed sorting of over 400 age-appropriate books and bookshelves.
\item Oversaw deployment of computer lab and library for student use
\end{rSubsection}
\end{rSection}

\pagebreak

\begin{rSection}{Relevant Coursework}

\begin{rSubsection}{Carnegie Mellon University}{}{Summer 2014}{}
\item 15-122 (Principles of Imperative Computation in C)
\item 21-127 (Concepts of Mathematics)
\end{rSubsection}

\begin{rSubsection}{University of California, Berkeley}{}{Fall 2015}{}
\item CS 61B (Data Structures in Java)
\item EE 16A (Designing Information Devices and Systems I)
\end{rSubsection}
\begin{rSubsection}{}{}{Spring 2016 (In Progress)}{}
\item EE 16B (Designing Information Devices and Systems II)
\item CS 198-47 (Ruby on Rails)
\end{rSubsection}

\end{rSection}

\begin{rSection}{Research}
\begin{rSubsection}{UC Berkeley Department of Computer Sciences}{January 2016\textminus Present}{Undergraduate Researcher, Computational Game Theory}{Berkeley, CA}
\item Identified main challenges in developing game solvers on distributed computing systems
\item Developed generalized algorithm for solving abstract strategy games using MPI
\item Deployed algorithm to the Savio Supercomputing Cluster for testing and analysis
\end{rSubsection}
\begin{rSubsection}{UC Berkeley Department of Nuclear Engineering}{February 2016\textminus Present}{Research Developer, RadWatch/DoseNet Project}{Berkeley, CA}
\item Maintain code base for wireless dosimeters to monitor real-time Bay Area radiation levels.
\item Upgrading Raspberry Pi hardware to include temperature and CO$_2$ sensors. 
\item Developing educational user interface to teach high school students about micro controllers.
\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}